---
title: "Reading Data from the web"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(rvest)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Do something simple

```{r}
x_vec = rnorm(30, mean = 5, sd = 3)

(x_vec - mean(x_vec)) / sd(x_vec)
```

We want a function to compute z-scores:

```{r}
z_scores = function(x){
  if (!is.numeric(x)){
    stop("Input must be numeric")
  }
  if (length(x) < 3){
    stop("Input must have at least 3 numbers")
  }
  z = (x - mean(x)) / sd(x)
  return(z)
}

z_scores(x_vec)
```

Try the function on some other things: (they should give errors)

```{r, error=TRUE}
z_scores(3)
z_scores("my name is rebekah")
z_scores(mtcars)
z_scores(c(TRUE, TRUE, FALSE, TRUE))
```

## Multiple Outputs

```{r}
mean_and_sd = function(x){
  if (!is.numeric(x)){
    stop("Input must be numeric")
  }
  if (length(x) < 3){
    stop("Input must have at least 3 numbers")
  }
  mean_x = mean(x)
  sd_x = sd(x)
  tibble(
    mean = mean_x,
    sd = sd_x
  )
}
```

Check that the function works:

```{r}
mean_and_sd(x_vec)
```

## Multiple Inputs

```{r}
sim_data = 
  tibble(
    x = rnorm(n = 100, mean = 4, sd = 3)
  )

sim_data %>% 
  summarize(
    mean = mean(x),
    sd = sd(x)
  )
```

Need to translate above into a function:

```{r}
sim_mean_sd = function(samp_size, mu = 3, sigma = 4){
  
 sim_data = 
  tibble(
    x = rnorm(n = samp_size, mean = mu, sd = sigma)
  )

sim_data %>% 
  summarize(
    mean = mean(x),
    sd = sd(x)
  ) 
}

sim_mean_sd(samp_size = 100, mu = 6, sigma = 3)

sim_mean_sd(samp_size = 100)
```

## Review Napoleon Dynamite

```{r}
url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

dynamite_html = read_html(url)

review_titles = 
  dynamite_html %>%
  html_nodes(".a-text-bold span") %>%
  html_text()

review_stars = 
  dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-rating") %>%
  html_text() %>%
  str_extract("^\\d") %>%
  as.numeric()

review_text = 
  dynamite_html %>%
  html_nodes(".review-text-content span") %>%
  html_text() %>% 
  str_replace_all("\n", "") %>% 
  str_trim()

reviews = tibble(
  title = review_titles,
  stars = review_stars,
  text = review_text
)
```

What about the next page of reviews? We need to turn it into a function instead of continuously coppying and pasting.

```{r}
read_page_reviews = function(url){
  
  html = read_html(url)

review_titles = 
  dynamite_html %>%
  html_nodes(".a-text-bold span") %>%
  html_text()

review_stars = 
  dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-rating") %>%
  html_text() %>%
  str_extract("^\\d") %>%
  as.numeric()

review_text = 
  dynamite_html %>%
  html_nodes(".review-text-content span") %>%
  html_text() %>% 
  str_replace_all("\n", "") %>% 
  str_trim()

reviews = tibble(
  title = review_titles,
  stars = review_stars,
  text = review_text
)
reviews
}
```

Try the function:

```{r}
dynamite_url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=2"

read_page_reviews(dynamite_url)
```

Let's read a few pages of reviews:

```{r}
dynamite_url_base = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="

dynamite_urls = str_c(dynamite_url_base, 1:5)

all_reviews = 
  bind_rows(
    read_page_reviews(dynamite_urls[1]),
    read_page_reviews(dynamite_urls[2]),
    read_page_reviews(dynamite_urls[3]),
    read_page_reviews(dynamite_urls[4]),
    read_page_reviews(dynamite_urls[5])
)
```

## Mean Scoping Example

```{r, error=TRUE}
f = function(x){
  z = x + y
  z
}

x = 2
y = 2

f(x = y)

f = function(x1){
  z = x1 + x2
  z
}

x1 = 2

f(x1 = 2)
```

## Functions as arguements

```{r}
my_summary = function(x, summ_func){
  summ_func(x)
}

x_vec = rnorm(100, 3, 7)

mean(x_vec)

my_summary(x_vec, IQR)
```

